% 参考文献
\def\line{−\hspace*{-.7zw}−}

\begin{thebibliography}{99}
%\bibitem{*}内の * は各自わかりやすい名前などをつけて、
%論文中には \cite{*} のように使用する。
%これをベースに書き換えた方が楽かも。
%書籍、論文、URLによって若干書き方が異なる。
%URLを載せる人は参考にした年月日を最後に記入すること。


%\bibitem{hoge}
%hoge
% 背景と目的のところ
\bibitem{earth}IPCC, de Coninck, H., A. Revi, M. Babiker, P. Bertoldi, M. Buckeridge, A. Cartwright, W. Dong, J. Ford, S. Fuss, J.-C. Hourcade, D. Ley, R. Mechler, P. Newman, A. Revokatova, S. Schultz, L. Steg, and T. Sugiyama, 2018: Strengthening and Implementing the Global Response. In: Global Warming of 1.5°C. An IPCC Special Report on the impacts of global warming of 1.5°C above pre-industrial levels and related global greenhouse gas emission pathways, in the context of strengthening the global response to the threat of climate change, sustainable development, and efforts to eradicate poverty [MassonDelmotte,V., P. Zhai, H.-O. P\"{o}rtner, D. Roberts, J. Skea, P.R. Shukla, A. Pirani, W. Moufouma-Okia, C. P\'{e}an, R. Pidcock, S. Connors, J.B.R. Matthews, Y. Chen, X. Zhou, M.I. Gomis, E. Lonnoy, T. Maycock, M. Tignor, and T. Waterfield (eds.)]. 
\bibitem{Related-Research1} 笹 健児,一寺田 大介,永井 紀彦,河合 弘泰,``船体運動と沿岸波浪に基づくフェリー欠航の判断基準に関する検討'',日本航海学会論文集, 120号, pp.99-106, 2009.
\bibitem{Related-Research2} Shreya Agrawal, Luke Barrington, Carla Bromberg, John Burge, Cenk Gazen, and Jason Hickey, ``Machine learning for precipitation nowcasting from radar images'', arXiv preprint arXiv:1912.12132, 2019.
\bibitem{rainfull}Using Machine Learning to "Now-cast" Precipitation in High Resolution. \url{https://ai.googleblog.com/2020/01/using-machine-learning-to-nowcast.html}
\\最終閲覧日:2021/2/1
\bibitem{nowphas} ナウファス. https://www.mlit.go.jp/kowan/nowphas/ \\最終閲覧日:2020/9/14
\bibitem{anei} 安栄観光. http://www.aneikankou.co.jp/ \\最終閲覧日:2021/1/30
\bibitem{windy}windy.com. \url{https://www.windy.com/} \\最終閲覧日:2021/1/30
\bibitem{stan}安栄観光,安全管理規定,旅客船. \\ \url{http://www.aneikankou.co.jp/res/pc/pdf/company/legal/anzenkanri5.pdf} \\最終閲覧日:2020/9/14
\bibitem{optical-flow}David J. Fleet and Y. Weiss, ``Optical flow estimation'', In Handbook of Mathematical Models in Computer Vision, 2006.
\bibitem{persistence}S. Pulkkinen, D. Nerini, A. A. P\'{e}rez Hortal, C. Velasco-Forero, A. Seed, U. Germann, and L. Foresti. Pysteps: an open-source python library for probabilistic precipitation nowcasting (v1.0). Geoscientific Model Development, 12(10):4185-4219, 2019.
\bibitem{MRMA}Jian Zhang, Kenneth Howard, Carrie Langston, Brian Kaney, Youcun Qi, Lin Tang, Heather Grams, Yadong Wang, Stephen Cocks, Steven Martinaitis, Ami Arthur, Karen Cooper, Jeff Brogden, and David Kitzmiller. ``Multi-radar multi-sensor (mrms) quantitative precipitation estimation: Initial operating capabilities'', Bulletin of the American Meteorological Society, 97(4):621-638, 2016.
\bibitem{HRRR}Stanley G. Benjamin, Stephen S. Weygandt, John M. Brown, Ming Hu, Curtis R. Alexander, Tatiana G. Smirnova, Joseph B. Olson, Eric P. James, David C. Dowell, Georg A. Grell, Haidao Lin, Steven E. Peckham, Tracy Lorraine Smith, William R. Moninger, Jaymes S. Kenyon, and Geoffrey S. Manikin, ``A north american hourly assimilation and model forecast cycle: The rapid refresh''. Monthly Weather Review, 144(4):1669-1694, 2016.
%chapter2
\bibitem{Yann LeCun}Y. LeCun, L. Bottou, Y. Bengio, and P. Haffner, ``Gradient- based learning applied to document recognition'', Proceed-ings of the IEEE, 86(11):2278-2324, 1998. 
%chapter4


\end{thebibliography}


